### 2021-12-03 documentos/intro.tex
the magic is real
Arrrrgggg
etc

\section{Introduction} % {{{
Several PRA articles go straight into matter. I guess we will write what we have to write
% }}}

>>>>

\section{Introduction} % {{{
Several PRA articles go straight into matter. I guess we will write what we have to write

Creo que puede quedar bonito, honesto y util si comenzamos motivando el
problema desde un punto de vista matemático, y luego seguimos platicando de las
consecuencias físicas, es decir mostrando que el problema como lo planteamos
tiene aplicaciones practicas.

Generalization of \textit{completely decoherence Pauli channels}, such as completely dephasing,
\begin{equation}
\rho \mapsto \rho_{00}\projj{0}+\rho_{11}\projj{1},
\end{equation}
and \textit{completely depolarizing},
\begin{equation}
\rho \mapsto \frac{\one}{2} \tr \rho,
\end{equation}
These channels correspond in collapsing the Bloch sphere into a line and a point, respectively. [...] Other families of channels inspired in leaving 
% }}}
